### 2025-09-14 paper/fig/scigen-1805.02474v1-10-src.tex
Import source directly into figure.

\begin{figure}[h]
    \small
    {\lstinputlisting[language=Fluid,mathescape=false]{../website/authoring-assistant/fluid/1805.02474v1-10.fld}}
    \vspace{-0.5em}
    \caption{Source code for \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}

>>>>

\begin{figure}[h]
    \small
    \begin{lstlisting}[language=Fluid,mathescape=false]
"""
	As shown in Table 3, BiLSTM gives significantly ${trendWord (model "BiLSTM" tableData).acc (model "LSTM" tableData).acc betterWorse} accuracies compared to uni-directional LSTM2, with the training time per epoch ${trendWord (model "BiLSTM" tableData).time_s (model "LSTM" tableData).time_s growShrink} from ${numToStr (model "LSTM" tableData).time_s} seconds to ${numToStr (model "BiLSTM" tableData).time_s} seconds. Stacking 2 layers of BiLSTM gives ${trendWord (model "2 stacked BiLSTM" tableData).acc (model "BiLSTM" tableData).acc improve} to development results, with a ${trendWord (model "2 stacked BiLSTM" tableData).time_s (model "BiLSTM" tableData).time_s smallerHigher} time of ${numToStr (model "2 stacked BiLSTM" tableData).time_s} seconds. 3 layers of stacked BiLSTM ${trendWord (model "3 stacked BiLSTM" tableData).acc (model "BiLSTM" tableData).acc improve} the results. In contrast, S-LSTM gives a development result of ${numToStr (model "S-LSTM" tableData).acc} %, which is significantly ${trendWord (model "S-LSTM" tableData).acc (model "2 stacked BiLSTM" tableData).acc betterWorse} compared to 2-layer stacked BiLSTM, with a ${trendWord (model "S-LSTM" tableData).param (model "2 stacked BiLSTM" tableData).param smallerHigher} number of model parameters and a ${trendWord (model "S-LSTM" tableData).time_s (model "2 stacked BiLSTM" tableData).time_s shorterLonger} time of ${numToStr (model "S-LSTM" tableData).time_s} seconds.  We additionally make comparisons with stacked CNNs and hierarchical attention (Vaswani et al., 2017), shown in Table 3 (the CNN and Transformer rows), ${(findWithKey' "time_s" (minimum (map (fun y -> y.time_s) tableData)) tableData).model} is the ${let pos = findIndex "model" "CNN" (insertionSort (fun a b -> a.time_s < b.time_s) tableData) in rankLabel "most efficient" pos} among all models compared, with the ${let pos = findIndex "model" "CNN" (insertionSort (fun a b -> a.param < b.param) tableData) in rankLabel "smallest" pos} model size. On the other hand, a 3-layer stacked CNN gives an accuracy of ${numToStr (model "3 stacked CNN" tableData).acc} %, which is also the ${let pos = findIndex "model" "CNN" (insertionSort (fun a b -> a.time_s < b.time_s) tableData) in rankLabel "lowest" pos} compared with BiLSTM, hierarchical attention and S-LSTM. The ${let pos = findIndex "model" "S-LSTM+Attention" (insertionSort (fun a b -> b.acc < a.acc) tableData) in rankLabel "best" pos} performance of hierarchical attention is obtained by S-LSTM+Attention in terms of both accuracy and efficiency. S-LSTM gives significantly ${trendWord (model "S-LSTM" tableData).acc (model "CNN" tableData).acc betterWorse} accuracies compared with both CNN and hierarchical attention. Table 3 additionally shows the results of BiLSTM and S-LSTM when external attention is used  Attention leads to improved accuracies for both BiLSTM and S-LSTM in classification, with S-LSTM still ${trendWord (model "S-LSTM" tableData).acc (model "BiLSTM" tableData).acc underOverPerforming} BiLSTM significantly.
"""
    \end{lstlisting}
    \vspace{-0.5em}
    \caption{Source code for \figref{scigen-example-website}}
    \label{fig:fluid-example-paragraph}
\end{figure}
